A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-06-02 03_Yield_MetaAnalysis.Rmd
add stability analysis

>>>>

## Meta-analysis stability test

To check the stability in the network analysis we will rerun the chosen model 15 times. 
Each run, one of the 15 trials will be excluded from the analysis to detect if any estimates varied significantly indicating an unstable network meta-analysis.
```{r stability}
stab_PM_mv <- 
   lapply(unique(PM_dat_Y$trial_ref), function(Trial){

      #subset to remove a trial
      dat <- filter(PM_dat_Y, trial_ref != Trial)

      PM_mv <- rma.mv(
         yi = grain_yield.t.ha.,
         V = vi,
         mods = ~ spray_management,
         method = "ML",
         random = list(~ spray_management | trial, ~ 1 | id),
         struct = "UN",
         control = list(optimizer = "optim"),
         data = dat
      )
   })

length(stab_PM_mv)
est <- lapply(stab_PM_mv, function(e1){
   data.frame(treat = rownames(e1$b),
              estimates = e1$b,
              p = as.numeric(reportP(e1$pval, P_prefix = FALSE,AsNumeric = TRUE)))
   })

stab_df <- data.table::rbindlist(est)
stab_df$Tnum <- rep(1:15, each = 6)

stab_df %>%
   ggplot(aes(Tnum, estimates, colour = treat))+
   geom_line()

stab_df %>%
   ggplot(aes(Tnum, p, colour = treat))+
   geom_line()+
   scale_y_log10()

stab_df %>%
   group_by(treat) %>%
   summarise(minEst = min(estimates),
             medEst = median(estimates),
             maxEst = max(estimates),
             minP = min(p),
             medP = median(p),
             maxP= max(p))
```

Trial 9 at missen flats changes the estimates the most when excluded due to the high number of reps
```{r}
unique(PM_dat_Y$trial_ref)[9]
```

### Between study heterogeneity
Calculation of I^2
```{r}
W <- diag(1/(PM_dat_Y$vi))
X <- model.matrix(PM_mv)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
100 * sum(PM_mv$sigma2) / (sum(PM_mv$sigma2) + (PM_mv$k-PM_mv$p)/sum(diag(P)))

100 * PM_mv$sigma2 / (sum(PM_mv$sigma2) + (PM_mv$k-PM_mv$p)/sum(diag(P)))
```
This indicates that approximate amount of total variance attributed to trials/ clusters is 99%, which is very high. 
However given that many of the means included in the model contained an accompanying sample variance of zero, this might have been expected.
